Disk Heating, Galactoseismology, and the Formation of Stellar Halos

### 2017-06-26 paper/paper.tex
add chrevin stuff

\begin{figure}[t]
\centering
%\includegraphics[width=3 cm]{logo-mdpi}
\caption{\label{fig:chervin}
}
\end{figure}

Figure \ref{fig:chervin} illustrates these ideas with the results of simulations from our own recent work.
We extended the prior theoretical backdrop that looked at Mon/GASS to examine whether the extreme locations of TriAnd 1/2 could fit within the same picture using simulations of a disk disturbed (separately) by satellites on orbits that mimic those expected for the Large Magellanic Cloud and Sagittarius \cite{laporte16}.
With different masses and orbits (and consequently different interaction  strength, timings, and durartions) these satellite necessarily induced distinct but overlapping signatures.
In  more recent work, we found that a model that was capable of reproducing the scales of the observed disturbances (radial wavelength and  amplitude in space, as well as magnitude of offsets in velocity locally) needed:
the  interaction of Sgr with the disk of the Milky Way to be followed for several passages longer than prior work;
Sgr to have of sufficient initial mass and density to impact the disk in the last Gigayear with a remaining mass of ???;
and the disk to be realized with stars existing as far out as ???kpc form the Galactic center in order to populate the regions corresponding to TriAnd 1/2.
The interaction with the LMC modified the overall morphology of the structures induced, but was not sufficient alone to explain their properties.
The full details of these results will be discussed in an upcoming paper (Laporte et al, 2017).

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[width=5 in]{figures/simulation.pdf}
\caption{\label{fig:chervin}
}
\end{figure}

Figure \ref{fig:chervin} illustrates these ideas with the results of simulations from our own recent work.
We extended the prior theoretical backdrop that looked at Mon/GASS to examine whether the extreme locations of TriAnd 1/2 could fit within the same picture using simulations of a disk disturbed (separately) by satellites on orbits that mimic those expected for the Large Magellanic Cloud and Sagittarius \cite{laporte17}.
With different masses and orbits (and consequently different interaction  strength, timings, and durartions) these satellite necessarily induced distinct but overlapping signatures.
In  more recent work, we found that a model that was capable of reproducing the scales of the observed disturbances (radial wavelength and  amplitude in space, as well as magnitude of offsets in velocity locally) needed:
the  interaction of Sgr with the disk of the Milky Way to be followed for several passages longer than prior work;
Sgr to have of sufficient initial mass and density to impact the disk in the last Gigayear with a remaining mass of $\sim3\times10^{9} M_{\odot}$;
and the disk to be realized with stars existing as far out as ???kpc form the Galactic center in order to populate the regions corresponding to TriAnd 1/2.
The interaction with the LMC modified the overall morphology of the structures induced, but was not sufficient alone to explain their properties.
The full details of these results will be discussed in an upcoming paper (Laporte et al, 2017).
